### 2021-11-12 NSF2021/Description/specificaim1.tex
Hola

The hydrophobic interactions come from the tendency 
of particles to minimize the free energy of the structure of
the surrounding water molecules.  
Experimental measurements suggest that the free energy functional
take the form 
\begin{equation}
\label{eq:free_energy}
F[u] = C \int_{\Omega}  \rho |\nabla u|^2 + \rho^{-1} f(u) \,dx
\end{equation}
where
$u$ is an order parameter for the structure of water,
$\rho$ is a decay length,
$C$ is a constant, and $f(u)$ is a potential.
Hydrogen-bond persistence times are on the order of picoseconds \cite{MaGa13}.
Since waters reorient 
on a time scale much smaller than for the particle motion, 
then at each moment in time $u$ minimizes $F[u]$ and satisfies 
\begin{equation}
\label{eq:SL}
-\rho^2 \Delta u + f'(u) = 0  \text{ in } \Omega,\quad u = g
\text{ on } \Omega.
\end{equation}
The boundary condition $g$ that imposes 
the water structure at the water-hydrocarbon interfaces.
It is a material label that is transported with the particle motions.

>>>>

The hydrophobic interactions come from the tendency 
of particles to minimize the free energy of the structure of
the surrounding water molecules.  
Experimental measurements suggest that the free energy functional
take the form 
\begin{equation}
\label{eq:free_energy}
F[u] = C \int_{\Omega}  \rho |\nabla u|^2 + \rho^{-1} f(u) \,dx
\end{equation}
where
$u$ is an order parameter for the structure of water,
$\rho$ is a decay length,
$C$ is a constant, and $f(u)$ is a potential.
Hydrogen-bond persistence times are on the order of picoseconds \cite{MaGa13}.
Since waters reorient 
on a time scale much smaller than for the particle motion, 
then at each moment in time $u$ minimizes $F[u]$ and satisfies 
\begin{equation}
\label{eq:SL}
-\rho^2 \Delta u + f'(u) = 0  \text{ in } \Omega,\quad u = g
\text{ on } \Omega.
\end{equation}
The boundary condition $g$
is a material label that is transported with the particle motions
(Figure \ref{fig:bcs}).
\begin{wrapfigure}[12]{r}{0.65\textwidth}
  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPA.pdf}
  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPB.pdf}
  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPC.pdf}  
\caption{
  Boundary conditions characterize the type of water structure:
  an amphiphilic particle (left),
  a hydrophobic particle with anisotropic intensity (middle),
  a water structure with plus/minus polarity (right).
  The dashed curve is the boundary of the disk and the arrow its
  director. 
}
\label{fig:bcs}
\end{wrapfigure}
